GlasSees - Providing Context Menus for the Real World Through Head-Worn Infrared Targeting

### 2013-09-18 doc/sigchi14/introduction.tex
figure cpation

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/teaser.jpg}
\caption{Using an augmented head-worn device (1), users can control smart home appliances (2) using head orientation targeting. A near-eye display (3) then shows an appliance control UI, which users navigate through multitouch gestures.}
\label{fig:teaser}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/teaser.jpg}
\caption{Using an augmented head-worn device (1), users can control smart home appliances (2) with head orientation targeting. A near-eye display then shows an appliance control UI (3), which users navigate through multitouch gestures.}
\label{fig:teaser}
\end{figure}
